Fourmile Calibrations and Output

### 2024-08-12 compare_luca_runs.Rmd
updated total volume of water for annual and fixed rd/rg seasonal sums

```{r, fig.width = 10}

# function to read files, remove top rows, paste site name
read_cals <- function(df, name){
    df <- df %>%
      slice(-c(1:9, 146:277)) %>%
      separate(Parameter, c("Parameter", "value"), sep = ",") %>%
      drop_na() %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)

@@

# boxplots
plot_params <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- params %>%
    filter(param == param_name)

@@

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}

plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

@@

# boxplots
plot_burnparams <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- burn_params %>%
    filter(params == param_name)

>>>>

```{r, fig.width = 10}
# function to read files, remove top rows, paste site name
read_cals <- function(df, name){
    df <- df %>%
      slice(-c(1:9, 146:277)) %>%
      separate(Parameter, c("Parameter", "value"), sep = ",") %>%
      drop_na() %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)

@@

lapply(name, plot_params)
```

## Box plots

```{r, fig.width = 10}
# boxplots
plot_params <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- params %>%
    filter(param == param_name)

@@

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

@@

lapply(name2, plot_burnparams)
```

## Burned box plots

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
# boxplots
plot_burnparams <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- burn_params %>%
    filter(params == param_name)

### 2024-08-12 fourmile_outputs_2013edits.Rmd
updated total volume of water for annual and fixed rd/rg seasonal sums

## Cumulative Q

@@

flow_cumq <- flow_pivot %>%
  mutate(month = month(date)) %>%
  filter(month %in% c(4:9)) %>%
  dplyr::select(-month) %>%
  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  group_by(cal_run, year(date)) %>%
  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
  #rename(year = 4) %>%
  mutate(year = as.factor(year)) %>%
  ungroup()

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'cumulative Q (m3s)')} %>%
    ggplotly()
}

@@

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2') +
  theme(text = element_text(size = 20))

@@

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG') +
  theme(text = element_text(size = 24))

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Annual sum') +
  labs(y = 'Total volume (m3)')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Annual sum') +
  labs(y = 'Total volume (m3)')

@@

#group by season and get max sums by season
flow_season <- gw %>%
  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
  mutate(month = month(date)) %>%
  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
                            month %in% c(7,8) ~ 'monsoon',
                            month %in% c(9,10,11,12) ~ 'baseflow_fall',
                            month %in% c(1,2) ~ 'baseflow_winter')) %>%
  group_by(source, year, season) %>%
  summarize(yr_season_RD1 = max(RD1cumsum),
            yr_season_RD2 = max(RD2cumsum),
            yr_season_RG1 = max(RG1cumsum),
            yr_season_RG2 = max(RG2cumsum)) %>%
            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  #geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season) +
  ggtitle('RD/RG annual sums') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size = 20)) +
  labs(y = 'Total flow (m3)')

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season + flow_type, scales = 'free') +
  ggtitle('Seasonal sums') +
  theme_bw() +
  theme(text = element_text(size = 20)) +
  labs(y = 'Total flow (m3)')

>>>>

## Cumulative volume

@@

flow_cumq <- flow_pivot %>%
  mutate(month = month(date)) %>%
  filter(month %in% c(4:9)) %>%
  dplyr::select(-month) %>%
  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(vol_m3 = q_m3s * 86400) %>% 
  group_by(cal_run, year(date)) %>%
  mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>%
  #rename(year = 4) %>%
  mutate(year = as.factor(year)) %>%
  ungroup()

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_2011"="seagreen",
                                            "grid_2012"="seagreen2",
                                            "grid_2013"="steelblue",
                                            "grid_2014"='dodgerblue',
                                            "grid_2015" = "cyan3",
                                            'grid_2016' = 'blue',
                                            'grid_2017' = 'blue4',
                                            'grid_2018' = 'cadetblue',
                                            'grid_2019' = 'lightgreen',
                                            'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            "statn_2011"="maroon",
                                            "statn_2012"="deeppink4",
                                            "statn_2013"="deeppink",
                                            "statn_2014"='purple',
                                            "statn_2015" = "mediumorchid1",
                                            'statn_2016' = 'indianred',
                                            'statn_2017' = 'sienna',
                                            'statn_2018' = 'salmon2',
                                            'statn_2019' = 'mediumpurple1',
                                            'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

@@

- **Different units than streamflow (cms) and volume (m3)** 
- **All in mm**

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD1 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RD2 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RG1 (mm)')

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RG2 (mm)')

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1 (mm)') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2 (mm)') +
  theme(text = element_text(size = 20))

@@

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG (mm)') +
  theme(text = element_text(size = 24))

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Annual sum') +
  labs(y = 'mm of water')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Annual sum') +
  labs(y = 'mm of water')

@@

#group by season and get max sums by season
flow_season <- gw %>%
  dplyr::select(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w, date, year, source) %>%
  mutate(month = month(date)) %>%
  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
                            month %in% c(7,8) ~ 'monsoon',
                            month %in% c(9,10,11,12) ~ 'baseflow_fall',
                            month %in% c(1,2) ~ 'baseflow_winter')) %>%
  group_by(source, year, season) %>%
  mutate(yr_season_RD1 = cumsum(catchmentRD1_w),
            yr_season_RD2 = cumsum(catchmentRD2_w),
            yr_season_RG1 = cumsum(catchmentRG1_w),
            yr_season_RG2 = cumsum(catchmentRG2_w)) %>%
  summarize(sumRD1 = max(yr_season_RD1),
            sumRD2 = max(yr_season_RD2),
            sumRG1 = max(yr_season_RG1),
            sumRG2 = max(yr_season_RG2)) %>%
            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'mm_water')

flow_season %>%
  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  #geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season) +
  ggtitle('RD/RG sums (mm)') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD/RG sums (mm)')

flow_season %>%
  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season + flow_type, scales = 'free') +
  ggtitle('Seasonal sums') +
  theme_bw() +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD/RG seasonal sums (mm)')
